Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels

### 2018-05-16 articles/formalism/sections/kernel_paintbrush.tex
New spiral figure and notation standardization
added text to discussion of kernel paintbrush

\section{Intuition for the polarization structure of magnetized filaments}
\begin{figure}
  \includegraphics[width=0.5\columnwidth]{line.pdf}
  \includegraphics[width=0.5\columnwidth]{spiral.pdf}
  \caption{
    The polarization signals of toy filament structures.
    In a filament organized perfectly along a magnetic field line, the polarization will be perpendicular to the filament direction.  The $E/B$ modes of filaments are in some ways easier to think about than the Stokes parameters.
    Left panels: in a straight filament, the E-mode is positive along the filament and at the ends, but negative along the sides.  B-modes are only non-zero at the ends.  Right panels: in a curved filament, the E-mode is again positive along the filament.  Outside the filament, the $E$-mode is more negative on the interior of the curve than the exterior.  The $B$-modes are again non-zero only at the ends, and are akin to the straight filament case.
    In all images, the longitude increases to the left (sky convention).}
  \label{fig:polfilaments}
\end{figure}

Naturally describes the reason for a positive T/E correlation.  Figure~\ref{fig:polfilaments}.

>>>>

\paragraph{Polarization signature of magnetized filaments}
The real space kernels give us a better intuitive understanding of the $E/B$ modes associated with physical objects.  For example, a simple model for a magnetize filament has the magnetic field threaded along a linear gas overdensity.  Precession of the dust grains around the magnetic field leads to a net polarization perpendicular to the magnetic field (and to the filament overall).  For a filament aligned North--South, the polarization will be horizontal or $Q<0$, $U=0$ (left pane of \fig{fig:polfilaments}.  The Green's function kernels for horizontal polarization are rotated by 90 degrees relative to the components of $\cal{M}_G$ in \fig{fig:vis_kernel}.

The kernel can be thought of as the orientable nib of a calligraphy stylus, and traced along the filament.  The positive components for the $E$ part of the Green's function align and reinforce along the filament, and so the filament is highlighted in $E>0$.  Since the overdensity will also have emission in total intensity, this naturally predicts a positive $T/E$ correlation for magnetized filaments.  The $E$ pattern is somewhat negative along the outside of the filament, also a consequence of the kernel shape.

The $B$ part of the Green's function, traced along the filament, cancels itself except at the filament ends.  This results in a non-zero $B$ pattern for the filament, positive on the North-East and South-West, and negative in the North-West and South-East.  \revisit{The non-zero $B$ result is somewhat surprising given that the polarization pattern is invariant under parity.}
Because the scalar polarization descriptions are coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.
The description is also intuitive if we distort the shape of the filament.  If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will council, and we are left with a pure $E$ pattern.  
The same general description holds for a spiral-shaped filament.  The filament is highlighted by positive $E>0$.  The $E$-pattern is more negative on the interior of a curve than on the exterior, and more so for a tighter radius of curvature.

\begin{figure}
  \includegraphics[width=0.5\columnwidth]{line.pdf}
  \includegraphics[width=0.5\columnwidth]{spiral.pdf}
  \caption{
    The polarization signals of toy filament structures.
    In a filament organized perfectly along a magnetic field line, the polarization will be perpendicular to the filament direction.  The $E/B$ modes of filaments are in some ways easier to think about than the Stokes parameters.
    Left panels: in a straight filament, the E-mode is positive along the filament and at the ends, but negative along the sides.  B-modes are only non-zero at the ends.  Right panels: in a curved filament, the E-mode is again positive along the filament.  Outside the filament, the $E$-mode is more negative on the interior of the curve than the exterior.  The $B$-modes are again non-zero only at the ends, and are akin to the straight filament case.
    In all images, the longitude angle increases to the left (East in sky convention).}
  \label{fig:polfilaments}
\end{figure}

  Figure~\ref{fig:polfilaments}.
